\Large \bf Cyclone: Warp Speed Replication for Key Value Stores

### 2017-04-20 paper/paper.tex
Updates to paper.

\subsection{Flash Log}
TBD: talk about why we don't need group commit.
\section{Horizontal Scaling}

>>>>

\subsection{Flash Log}
Cyclone is designed to use only limited amounts of NVM and drains log entries
down into a log placed on a flash SSD - that we term the flashlog. The flashlog
is written out in segments of configurable size (we use 128KB segments). A
segment buffer is prepared in memory (volatile DRAM) using the layout shown in
Figure~\ref{fig:flashlog_page}. We do not allow objects in the flashlog to cross
a 4KB boundary - linking multiple objects together with a special flag encoded
into the size if necessary. We flush log segments out to the log file using
asynchronous direct IO, and therefore we fill one log segment buffer while
keeping IO to another one outstanding to the flash drive. To avoid having to do
a synchronous metadata flush, we preallocate (using the posix\_fallocate call) a
gigabyte worth of zero filled disk pages at the end of a file, at a time.

In order to recover from a crash, we make two important assumptions about the
underlying SSD. First, we assume that 4KB is the \emph{minimum} atomic unit for
updating pages on the SSD even under power failure i.e. there are no shorn
writes on a 4KB page~\cite{shorn_writes}. We also assume that the SSD has power
loss data protection meaning that writes cached in the drive's volatile cache
are written to the SSD using a backup capacitor in the event of power failure -
a property of many data center class SSDs today, including the Intel DC P3600
SSD we use in our evaluation. Together these two assumptions mean that we can
recover a consistent prefix of the log on a power failure.

We move log entries from the head of the NVM log to the flashlog buffers in FIFO
order. THe NVM log entry is only actually removed then the IO for the
corresponding flashlog page is complete. This means that during recovery we can
have the same log entry both in the NVM log and the flashlog, a condition that
can be detected by examining the RAFT related information that is embedded as
part of the logged packet.

\begin{figure}
  \centering
  \includegraphics[scale=0.3]{figures2/flashlog_page.pdf}
  \caption{Flashlog segment}
  \label{fig:flashlog_page}
\end{figure}

The fact that we can immedately absorb updates into an NVM log and only move
them to the flashlog in suitable units for block IO solves a common problem with
logging to secondary storage - the need to do group commit. Logging systems
often wait to collect a batch of entries to write to secondary storage trading
latency for throughput. This is unnecessary in Cyclone as it
effectively makes use of directly attached NVM with a two level log that removes
the need to make this tradeoff.

\section{Horizontal Scaling}
